Posterior comparison methods

### 2022-11-02 src/explore_posterior-comparison/posterior-comparison.Rmd
Add KS to posterior-comparison

>>>>

```{r}
n <- length(unique(samples_mcmc$index))

ks_gaussian_mcmc <- lapply(1:n, function(i) {
  samples_gaussian_i <- filter(samples_gaussian, index == i)$value
  samples_mcmc_i <- filter(samples_mcmc, index == i)$value
  inf.utils::ks_test(samples_gaussian_i, samples_mcmc_i)
})

ks_laplace_mcmc <- lapply(1:n, function(i) {
  samples_laplace_i <- filter(samples_laplace, index == i)$value
  samples_mcmc_i <- filter(samples_mcmc, index == i)$value
  inf.utils::ks_test(samples_laplace_i, samples_mcmc_i)
})

ks_results <- bind_rows(
  bind_rows(ks_gaussian_mcmc, .id = "index") %>%
    mutate(type = "gaussian"),
  bind_rows(ks_laplace_mcmc, .id = "index") %>%
    mutate(type = "laplace")
)

ks_results %>%
  select(index, D, type) %>%
  pivot_wider(
    names_from = type,
    values_from = D
  ) %>%
  ggplot(aes(x = laplace, y = gaussian)) +
    geom_point(alpha = 0.5) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
    lims(x = c(0, 1), y = c(0, 1)) +
    labs(x = "KS(laplace, mcmc)", y = "KS(gaussian, mcmc)") +
    theme_minimal()

ks_results %>%
  group_by(type) %>%
  summarise(mean = mean(D)) %>%
  kable()
```
